Optimal management of a stochastically varying population when policy adjustment is costly

### 2013-11-07 inst/doc/policycosts/policycosts.tex
pdf

\documentclass[authoryear, review, 12pt]{elsarticle}
\usepackage{amssymb,amsmath,amsfonts,graphicx}
\bibliographystyle{elsarticle-harv}
%\usepackage{natbib} % already loaded by elsarticle
%\biboptions{sort&compress} % For natbib
%\usepackage{hyperref} % already loaded by elsarticle
%\hypersetup{breaklinks=true, pdfborder={0 0 0}}

\usepackage[hyphens]{url}

\usepackage{lineno}
\linenumbers

\usepackage{subfigure}
%\usepackage[nomarkers]{endfloat}
\renewcommand{\listoffigures}{} % but suppress these lists
\renewcommand{\listoftables}{} % suppress these lists

%% Redefines the elsarticle footer
\makeatletter
\def\ps@pprintTitle{%
\let\@oddhead\@empty
\let\@evenhead\@empty
\def\@oddfoot{\it \hfill\today}%
\let\@evenfoot\@oddfoot}
\makeatother
% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in

\usepackage{microtype}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{arabic}

\usepackage[pdftex, usenames]{color}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\newcommand{\cdb}[1]{{\it \color{darkgreen} #1}}

\begin{document}
\begin{frontmatter}
\title{Policy Costs}
\author[cpb]{C. Boettiger\corref{cor1}}
\ead{cboettig@ucdavis.edu}
\author[melbourne]{M. Bode}
\author[esp]{J. Sanchirico}
\author[utk-econ]{J. LaRiviera}
\author[cpb,esp]{A. Hastings}
\author[utk-eeb]{P. Armsworth}
\cortext[cor1]{Corresponding author}
\address[cpb]{Center for Population Biology, University of California, Davis, California 95616, USA}
\address[esp]{Department of Environmental Science \& Policy, University of California, Davis, CA 95616, USA}
\address[utk-econ]{Department of Economics, University of Tennessee, Knoxville, TN 37996, USA}
\address[utk-eeb]{Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville, TN 37996, USA}
\address[melbourne]{Australian Research Council Centre of Excellence for Environmental Decisions, University of Melbourne, School of Botany,
Parkville, Melbourne, VIC 3010, Australia}

\begin{abstract}
\cdb{Carl's comments \& questions added in green}
\end{abstract}
\begin{keyword}
  optimal control \sep management \sep stochastic dynamic programming \sep fisheries 
\end{keyword}

\end{frontmatter}

@@

\emph{Could use input from those most familiar with this literature to flush this out more.}

@@

(See Figure~\ref{fig:1} which motivates the importance of considering policy costs by comparing a theoretically optimal policy over time to a typical real world policy over time).

\begin{figure}[ht]
  \begin{center}
    \subfigure[Optimal Policy]{\includegraphics[width=.5\textwidth]{figure/optimal_harvest}\label{fig:1a}}
    \subfigure[Typical Policy]{\includegraphics[width=.5\textwidth]{figure/typical_policy}\label{fig:1b}}
  \end{center}
  \caption{\ref{fig:1a} shows a typical solution found by an optimal
  control solution by stochastic dynamic programming for the optimal catch
  quota in a managed fishery.  Note that the solution tends to track the
  noise, resulting in a highly variable policy.  \ref{fig:1b} shows the
  actual quotas set over the past decade for Bluefin tuna, which show
  great intertia to change despite considerable movement in the stock
  dynamics.  \cdb{Conceptual picture illustrating the need to account
  for costs to changing policy. Current images are just placeholders.
  B should be replaced with real data, perhaps tuna quotas from Paul.
  Should stock dynamics actually be shown?}}
  \label{fig:1}
\end{figure}

%Optimal management of ecosystems and natural resources often involves
%frequent adjustment of a control variable in response to the observed
%state of a system. When this control is set in a policy-making process,
%such as determining a fishing quota, it may be more costly to change
%the policy in response to new information than to continue with the
%status quo ~\citep{Bohm1974, Xepapadeas1992}.  A management strategy that
%is optimal when adjustment costs are free may be costly and inefficient
%when these costs are present.  Meanwhile, this inertia to policy change
%introduces a two-fold cost to optimal management solutions that account
%for it: once in direct costs of changing policy, and another in the
%differences from optimality.

\subsection{Types of real world policy costs}

\begin{itemize}
  \item A discussion of capital adjustment costs, smoothing, \emph{e.g.} \citet{Singh2006}.
  \item Historical context, \emph{e.g.} discussion of \citep{Bohm1974, Reed1979, Xepapadeas1992}.  
\end{itemize}
\subsection{Stochastic fisheries model}
\begin{itemize}
\item Historical context of the Reed (1979) model.  
\item Discuss the importance and relevance of stochastic, discrete time models, which frequently yield highly variable solutions since the policy tracks the shock.  
\end{itemize}

@@

\subsection{Model setup}

\begin{itemize}
  \item   Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics,
    \begin{equation} 
      X_{t+1} = Z_t \frac{A X_t}{1 + B X_t}, 
    \end{equation}
where $Z_t$ gives the stochastic shocks.  $Z_t$ may be distributed log-normally \footnote{though this violates the self-sustaining property of~\citet{Reed1979}, such that the optimal constant-escapement level $S$ in the stochastic model is greater than the optimal escapement in the deterministic scenario.}

\item   Fishing profit function 
  \begin{equation} 
    \Pi_0(x,h) = p h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \label{profit}
  \end{equation}
  where $h$ is the harvest level, $x$ the stock size, $h/x$ represents
  fishing effort, $p$ the price per unit harvest.  The coefficient $c_1$
  introduces a quadratic cost to effort, a typical way to introduce
  smoothing~\citep[\emph{e.g.}][]{Singh2006}.  For simplicity, we will consider $c_0 =
  c_1 = 0$.

\item
Policy cost function: L1, L2, fixed fee, asymmetric, are introduced
as modifications to the cost function that depend on the action
taken in the previous time-step.  (This makes the previous action part
of the state space).   All cost functions are characterized in terms
of the coupling coefficient $c_2$.  (Because $c_2$ takes different units
and strength of interaction under the different functional forms, it is
necessary to calibrate the choice of this coefficient such that these
penalties can be compared directly, as described in the next section.)

  \begin{align} 
    \Pi_{L_1}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \operatorname{abs}\left( h_t - h_{t-1} \right) \label{L1} \\
    \Pi_{L_2}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \left( h_t - h_{t-1} \right)^2 \label{L2} \\
    \Pi_{\textrm{fixed}}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \mathbb{I}(h_t, h_{t-1})  \label{fixed_fee} \\
    \Pi_{\textrm{asym}}(x_t,h_t, h_{t-1}) &= \Pi_0 + c_2 \operatorname{max}\left( h_t - h_{t-1}, 0 \right) \label{asym}
  \end{align}
  Where $\mathbb{I}(a,b) = 0$ for $a \neq b$ and  $\mathbb{I}(a,b) = 1$ for $a = b$.

\item   Economic discounting, boundary conditions, constraints, Bellman equation, SDP solution method on finite time horizon.  
\item   Choice of model parameters 
\end{itemize}

\subsection{Apples to apples comparisons}

% From Jake:

The fact that there is no uniform metric for comparing different functional forms of the penalty function complicates identifying the implications of various penalty functions on optimal management.  Put another way, it is unclear what parameter values should be used for each functional form in order to compare the relative effect of each penalty function on optimal management.  
To address this issue, consider the following rule for comparing functional forms inspired by Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).  By definition, adding a constraint, in the form of a penalty function, to the social planner’s objective function will reduce the NPV of the resource in addition to affecting the optimal management policy.  For example, each individual penalty function equation (3)-(6) is multiplied by a constant C2.  As the magnitude of the penalty function increases (e.g., C2 increases), the NPV value of the resource decreases.  Importantly, though, the rate at which the NPV is affected by a given increase in magnitude of the penalty function is different for different penalty functions.  One way to compare the relative impact of penalty functions on optimal management is to choose parameters for the penalty function that imply the same level of NPV conditional on optimal management.

Figure 2 shows this comparison criterion graphically.  Each curve plots the percentage change in NPV relative to the unconstrained problem for a given penalty function over different magnitudes of that penalty function, C2, given optimal management.  There are two important features in Figure 2.  First, the optimal management policy is not constant across penalty function.  This will be discussed in detail below.  Second, the rate of change in NPV as a function of the magnitude of the penalty function varies both within and across policies.  For example, the existence of a relatively small L2 penalty function dramatically affects the resource’s value initially but there is little marginal effect on NPV for relatively large L2 penalty functions.  Conversely, the rate of change in NPV for the fixed penalty function is roughly constant over all ranges of penalty function magnitudes.

To compare the impact of penalty functions on optimal management, we select penalty magnitudes that make the resource worth 80\% of its unconstrained value.   The dashed vertical lines in Figure 2 map the needed penalty function magnitude, C2, to each penalty function such that the resource is worth 80\% of its unconstrained value when optimally managed.  We choose 80\% somewhat arbitrarily but the method is applicable to any NPV level and the qualitative effects on management are robust for other levels.

Bovenberg, AL, Goulder LH, and Gurney DJ (2005).  “Efficiency Costs of Meeting Industry-Distributional  Constraints Under Environmental Permits and Taxes” RAND Journal of Economics. 36(4): 951-  971.

Bovenberg, AL, Goulder LH, and Jacobsen MR (2008).  “Costs of Alternative Policy Instruments in the    Presence of Industry Compensation Requirements” Journal of Public Economics. 92: 1236-1253.

%% end-Jake

We compare the impact of the different functional forms for the penalty
function at a value of the penalty scaling parameter in each model that
induces an equivalent net present value to the stock when optimally
managed under this penalty. This value represents the expected net
present value before the costs of policy adjustment are paid, Figure~\ref{fig:apples}

  \begin{figure}
    \begin{center}
\includegraphics[width=.8\textwidth]{figure/npv0.png}
\caption{\textbf{Net present value by functional form of penalty.} Horizontal axis shows the coefficient $c_2$ governing the magnitude of the policy cost, while vertical axis shows fraction of the stock value dissipated by the policy cost.  The horizontal line indicates a value of the stock that is 80\% of the adjustment-free value. Selecting the coefficient $c_2$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.  }
\label{fig:apples}
\end{center}
\end{figure}

\section{Results}
\subsection{Characterize and compare functional forms of costs}

Figure~\ref{fig:shapes} shows the impact the adjustment cost has on the optimal policy.  The $L_1$-norm costs tend to avoid small adjustments to the policy, resulting in long periods of constant policy followed by sudden bursts of adjustment.  In contrast, the $L_2$-norm tracks all of the changes made by the cost-free policy, but with smaller magnitude.  The fixed fee only makes large adjustments much like the $L_1$, as expected where the adjustment magnitude does not impact the cost.  Asymmetric ($L_1$) adjustment costs do not appear to show more directional bias than any of the symmetric costs.  Note that while the cost-free optimal strategy corresponds to a constant-escapement policy as derived in~\citet{Reed1979}, any of the policy-cost scenarios deviate from such a policy.  
    \cdb{
    \begin{itemize}
      \item All of these should use the same sequence of shocks.  
      \item Don't plot all four curves on the same graph.  
      \item Omit stock dynamics?
      \item Consider not violating the self-sustaining property, which should also guarantee that fishing never stops.   
    \end{itemize}
    }

\cdb{ In terms of a policy set on escapement instead of harvest, our solutions are actually more volatile than~\citet{Reed1979}.  Maybe this leads to a discussion of what the control policy should be defined in terms of (i.e. catch vs escapement)?  Surely the simplicity of the constant-escapement rule has led to it's popularity in some part due because that simplicity avoids adjustment costs?}

  \begin{figure}
    \begin{center}
      \subfigure[$L_1$]{\includegraphics[width=.45\textwidth]{figure/7258516896_5c89f034d5_o.png}\label{fig:L1}}
      \subfigure[$L_2$]{\includegraphics[width=.45\textwidth]{figure/7258563112_2f5f9ffecd_o.png}\label{fig:L2}}

      \subfigure[Fixed costs]{\includegraphics[width=.45\textwidth]{figure/7258506664_d6235e5f8e_o.png}\label{fig:fixed}}
      \subfigure[Asymmetric costs]{\includegraphics[width=.45\textwidth]{figure/7258432026_d6f8179f54_o.png}\label{fig:asym}}
  \end{center}
  \caption{Individual realizations of management under the different functional forms of adjustment costs.  \textbf{Green} lines show the cost-free optimal harvest levels, \textbf{black} lines show the corresponding stock dynamics under that management.  \textbf{Purple} lines show the optimal harvest level under the specified adjustment cost, under the same sequence of stochastic shocks as in the cost-free policy.  \textbf{Blue lines} show the resulting stock dynamics.
  } \label{fig:shapes}
\end{figure}

\subsection{Responses to increasing costs}

The comparisons shown in Figure~\ref{fig:shapes} are made at a fixed magnitude of the policy cost equal to 80\% of the net present value derived from the cost-free optimal strategy.  The different functional forms may also respond differently to an increasing magnitude of the adjustment cost.  To quantify the extent to which the policy cost decreases the volatility of the proposed policy, we calculate the variance in the fishing quota over time under each policy.  While a decrease in variance is typical of smoothing penalties and the $L_2$-norm, the patterns in Figure~\ref{fig:shapes} suggest that other functional forms still involve the same magnitude of variation, but decrease the frequency of adjustments.  To capture this behavior we calculate the autocorrelation of the policy as the adjustment cost increases.  These curves van be seen in Figure~\ref{fig:summarystats}.

\cdb{Perhaps not clear what is comparable here and what isn't.  Certainly we cannot compare the curves at the same value of $c_2$, as discussed in our apples to apples section.  Not clear that we can even compare the shape of the curves though -- for instance, given the units of $c_2$ for the $L_2$ norm are different than the other norms.  Perhaps the horizontal axis should be converted into percent of net present value of the adjustment free costs first?}

\cdb{Add additional plot: Is value a linear function of policy cost, or is there a sharp transition? }
%Must be nonlinear somewhere when adjustment costs exceed profits?

\begin{figure}
  \begin{center}
    \subfigure[Variance]{\includegraphics[width=.45\textwidth]{figure/6850042286_ef81b74acc_o.png}\label{fig:var}}
    \subfigure[Autocorrelation]{\includegraphics[width=.45\textwidth]{figure/6996165783_41c9894bdb_o.png}\label{fig:acor}}
    \caption{Variance and autocorrelation as a function of the magnitude of penalty, by penalty function}\label{fig:summarystats}
  \end{center}
\end{figure}

\subsection{Consequences of ignoring policy adjustment costs}

\begin{itemize}
  \item Distribution of profits and costs under a policy-cost scenario vs profits and costs under Reed solution, by penalty type. Figure~\ref{fig:profits_costs}.
  \item Distribution of net present value under the policy-cost scenario vs the Reed solution, Figure~\ref{fig:npv_dist}.  
\end{itemize}

\begin{figure}
  \begin{center}
    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440758_99645d6e5a_o.png}\label{fig:L1cost}}
    \caption{Ignoring the cost of policy adjustment results in greater profits from fishing, but even greater costs for adjusting the harvest quotas each year.  Costs and profits are shown for ignoring the adjustment costs (Reed solution, purple and blue) and accounting for the adjustment (green and red).  \cdb{Though only L1 shown for the moment, would probably show all four types.  Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:profits_costs}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \subfigure[L1]{\includegraphics[width=.45\textwidth]{figure/7751440918_3b54ff2397_o.png}\label{fig:L1npv_dist}}
    \caption{\textbf{The impact of ignoring policy costs}.  Distribution of net present value realized over 100 simulations when adjustment costs are ignored (blue), compared to when adjustment costs are optimally accounted for (red). \cdb{Though only L1 shown for the moment, would probably show all four types.  Possibly a table or box-and-whiskers style plot would be better?}}\label{fig:npv_dist}
  \end{center}
\end{figure}

Add two-by-two table of net present value accounting for:  ``Adjustment cost in policy calculation'' by ``adjustment cost in reality''?

\cdb{\textbf{Further things to look at?}
\begin{itemize}
  \item How are costs partitioned between policy adjustments and deviation from optimality? 
  \item Risk sensitivity: does policy inertia increase or decrease extinction risk? Does accounting for the policy cost increase or decrease extinction risk?  (only in cases where extinction is possible: \emph{e.g.} in large variance, outside of Reed's self-sustaining range.  Or Allee model)
\end{itemize}
}

\section{Discussion}
\cdb{Some possible things to discuss: could add others, could remove some.}
\begin{itemize}
\item   Comparison of the optimal policy solution to the Reed model
\item  Comparison between the different functional forms -- smoothing (L2)
  non-smoothing (L1), and de-stablizing (fixed).
\item   Induced costs (relative to free adjustment) vs direct costs (paid for adjusting) 
\item   Impact of symmetric vs asymmetric costs
\item   Contrast steady-state results to dynamic solutions under stochastic shocks.
\end{itemize}

>>>>

\documentclass{article}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\title{Optimal management of a stochastically varying population when policy adjustment is costly}

%\titlerunning{Short form of title}        % if too long for running head

\author{Carl Boettiger    \\
       Michael Bode      \\
        James N. Sanchirico \\
Jacob LaRiviere \\
Alan M. Hastings\\
Paul R. Armsworth
}

\maketitle

@@

@@

\emph{Develop a figure to insert here comparing quotas that were set to the stock size estimated at that time in the stock assessment for two different fish stocks. We choose the two stocks to highlight variation in how responsive management can be. Suggested halibut and bluefin tuna.}

Empirics suggest not always as responsive as Reed solution. Explore conditions under which that makes sense. Idea is that regulator’s objective sometimes may not be `raw' NPV, but rather NPV with some penalties on fast changes. Possible reasons: pure administrative transaction cost of changing policies (reaching agreement), fishermens' preferences for less variable quotas, processing plants' preferences for less variable quotas especially if tied into contracts for canning and so forth. But we do not know what functional form of any such policy adjustment costs takes and it will be a lot of work to estimate it. Here we explore several plausible candidate functional forms that each reflect different ways these policy adjustment costs could work. Would be good to know if differences between functional forms is particularly important.

@@

 Fish population dynamics / state equation.  We will assume Beverton-Holt dynamics with multiplicative environmental noise
    \begin{equation} 
      N_{t+1} = Z_t \frac{A N_t}{1 + B N_t}, 
\label{eq:state_equation}
    \end{equation}
where $N_t$ the stock size, $Z_t$ gives the stochastic shocks, which we assume are lognormally distributed and $A$ and $B$ are positive constants. HARVESTING SHOULD APPEAR IN THIS EQUATION.

We assume managers set an annual quota for harvesting $h_t$ (the control variable) after observing the stock size that year $N_t$ (the state variable), but while still being uncertain about future environmental conditions and stock sizes. Through time, this gives a time path of management actions ${\bf h}=(h_1,h_2,\dots)$ that depend on the stock sizes that were observed (a state dependent control rule).

We assume that managers choose annual quotas to maximize the expected net present value (NPV) of the fishery. We take as a base case the situation where there are no costs associated with policy adjustment and the managers' objective is
\begin{equation}
\max_{{\bf h}}\mathbf{ E} ( NPV_{0} )=\max_{{\bf h}} \sum_0^\infty \mathbf{E} \left( \displaystyle \frac{\Pi_0(N_t,h_t)}{(1+\delta)^{t+1}} \right)
\label{eq:objective}
\end{equation}
where $\mathbf{E}$ is the expectation operator, $\delta>0$ is the discount rate and $\Pi_0$ is the net revenue from operating the fishery in a given year. In this base case, we assume the annual net revenue from fishing is 
  \begin{equation} 
    \Pi_0(N_t,h_t) = p h_t -  c_0 E_t
\label{eq:annual_netrevenue}
  \end{equation}
  where $E_t$ represents
  fishing effort. We assume catch is proportional to stock size and effort expended fishing that year, $h_t=qE_tN_t$ and constant $q>0$ is the catchability coefficient. In Eqn.~\ref{eq:annual_netrevenue}, $p$ is the price per unit harvest and $c_0$ the cost of fishing and we assume $p>0$ and $c_0>0$.

Taken together this objective function (\ref{eq:objective}) and the state equation (\ref{eq:state_equation}) define a stochastic dynamic programming problem that we solve using backwards recursion via Bellman's equation. We denote the resulting state-dependent, optimal control as ${\bf h_0^*}$. PRESUMABLY YOU USED A FINITE TERMINAL TIME IN WHICH CASE WE NEED TO REVISE TO REFLECT HOW YOU HANDLED THAT.

\subsection*{Costs of policy adjustment}
We compare this base case to three alternative problem formulations, each reflecting different plausible functional forms that costs of policy adjustment could take. In each, we assume managers can adjust the quota set in the fishery $h_t$ in a given year and that any policy adjustment costs are associated with changes to this control variable.

First we assume that policy adjustment costs are directly proportional to the magnitude of the change in policy being proposed, such that larger changes to annual harvesting quotas incur greater policy adjustment penalties. Specifically, we replace $\Pi_0$ in the $NPV_0$ equation with 
\begin{equation}
  \Pi_{1}(N_t,h_t, h_{t-1}) = \Pi_0 - c_1  |  h_t - h_{t-1} | \,.
\end{equation}

Next we continue to assume that policy adjustment costs depend on the magnitude of the change in policy being proposed. However, we consider a case where this dependence is nonlinear with big changes in policy being disproportionately expensive:
\begin{equation}
  \Pi_{2}(N_t,h_t, h_{t-1}) = \Pi_0 - c_2 (  h_t - h_{t-1})^2 \,.
\end{equation}

Finally, we assume instead that there is a fixed cost associated with any adjustment of policy, regardless of how large that adjustment might be
\begin{equation}
  \Pi_{3}(N_t,h_t, h_{t-1}) = \Pi_0 - c_3 (1-\mathbf{I}(h_t, h_{t-1}))  \,,
\end{equation}
where indicator function $\mathbf{I}(h_t, h_{t-1})$ takes the value 1 if $h_t=h_{t-1}$ and zero otherwise. For each $\Pi_i$, we can then define a new objective function $NPV_i$ similar to that in Eqn.~\ref{eq:objective}.

Taken together with the state equation (Eqn.~\ref{eq:state_equation}), each of these new objective functions defines a different stochastic dynamic programming problem. Again, we solve them numerically using backwards recursion.  To include costs of policy adjustment, we expand the state space to include both the current stock size and the management action taken on the previous time step $(N_t,h_{t-1})$. For each new objective function $\max NPV_i$, we denote the corresponding optimal control policy $ {\bf h_i^*} $.

In addition in the Supplementary Material, we compare our results with a more conventional fisheries economic formulation in which additional costs are applied to the control variables themselves, as opposed to adjustments to the controls: $ \Pi_4 (N_t,h_t) = p h_t -  c_0 E_t-c_4E_t^2$. Additional costs of this form tend to have  a smoothing effect on optimal quotas, but also change the long-term average stock size or quota size that is optimal.

\subsection*{Choice of parameters}

Each of the policy adjustment cost function is characterized in terms
of a cost coefficient $c_i$.  However, $c_i$ takes different units for each  functional form. Therefore, if seeking to compare the relative effect of each penalty function on optimal management, it is unclear what parameter values should be used. To address this issue, we calibrate choices of $c_i$ so that each has a comparable impact on the optimal net present value of fishery, broadly following the example of Bovenberg, Goulder and Gurnery (2005) and Bovenberg, Goulder and Jacobsen (2008).

Figure 1 shows the calibration graphically.  Each curve plots the change in maximum expected NPV for a given penalty function as the penalty cost parameter is increased. In each case, the figure shows maximum expected NPV with policy adjustment costs as a proportion of the maximum expected NPV available in the basic problem $NPV_0({\bf h_0^*})$ without policy adjustment costs.

To compare the impact of penalty functions on optimal management across the different functional forms, we select penalty cost coefficients that induce the same reduction in maximum expected NPV. For example, the dashed vertical lines in Figure 1 map the needed cost coefficient $c_i$, for each penalty function, such that the fishery is worth 80\% of its unconstrained value when optimally managed.

Other parameters in the model are chosen - HOW?

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_1}

\end{knitrout}

\caption{\textbf{Expected net present value by functional form of penalty.} Horizontal axis shows the coefficient $c_i$ governing the magnitude of the policy cost, while vertical axis shows fraction of the maximum expected net present value dissipated by the policy cost.  The horizontal line indicates a value of the stock that is 80\% of the maximum expected value in the absence of policy adjustment costs, $NPV_0({\bf h_0^*})$. Selecting the coefficient $c_i$ corresponding to this value in each functional form allows us to make consistent comparisons across the different functional forms of policy costs.  }
\end{figure}

\section{Results}
\subsection*{Effect of policy adjustment costs on optimal quotas and stock sizes}
Figure 2 shows the impact that the adjustment cost has on the optimal policy.   Each panel is generated against the same sequence of random shocks so that they can be compared directly. Figure 3 (TO COME) shows the corresponding stock sizes.  In each case, the optimal solution without any adjustment cost is shown in black and the policy induced by optimization under the given adjustment penalty (equivalent to a 25\% reduction in maximum expected NPV) is overlaid in blue.

When considering the first formulation of policy adjustment costs ($\Pi_1$), the first  panel of Figure 2 shows a typical pattern, in which the optimal policy tends to avoid small policy adjustments, resulting in long periods of constant policy followed by sudden bursts of adjustment. This results in a relatively step-like policy pattern.  In contrast, the second formulation $\Pi_2$ disproportionately penalizes large policy adjustments. The corresponding optimal policy tracks all of the changes made by the cost-free policy, but with smaller magnitude.  This results in a smoother $h_t$ curve, one that undershoots the larger oscillations seen in the cost-free optimum in favor of a policy that changes incrementally each yearl.  Finally, the optimal policy for the third, `fixed fee' formulation ($\Pi_3$) only makes large adjustments, as one might expect, because the magnitude of the adjustment made is not reflected in the resulting penalty.  Whereas the optimal solution for $\Pi_1$ attempts to accommodate the large oscillations at the end of the period shown (time steps $t=47-49$) with a constant quota in between the extremes, the fixed fee version takes the opposite approach of one very large swing. MORE DETAILING TO COME WHEN WE HAVE THE FIGURES

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_2}

\end{knitrout}

  \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_3}

\end{knitrout}

  \caption{Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.}
\end{figure}

The comparisons shown in Figure 2 are for one realization (i.e. a particular sequence of random number draws representing environmental variability) and are made for a particular magnitude of policy adjustment costs equal to 25\% of the maximum expected net present value in the base case ($NPV_0({\bf h_0^*})$). Figure 4 generalizes to show how optimal harvest levels and corresponding optimal stock sizes are affected by the magnitude of the costs of policy adjustment. This time we show summary statistics across 50 replicate sets of environmental conditions. We show the impact of policy adjustment costs on the variance of both harvests and stock sizes through time; on the autocorrelation of harvests and stock sizes through time; and on the cross-correlation of harvests and stock sizes through time.  (COMPARABLE FIGURES FOR OPTIMAL STOCK SIZES AND CROSS-CORRELATIONS OF THE TWO TO COME.)

We see that TO COME WHEN WE HAVE THE FIGURES

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_4a}

\end{knitrout}

\caption*{Figure 4a: Variance of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_4b}

\end{knitrout}

\caption*{Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_5a}

\end{knitrout}

\caption*{Figure 5a: Variance of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_5b}

\end{knitrout}

\caption*{Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

\subsection*{Consequences of policy adjustment costs}

Next we examine the consequences either of ignoring policy adjustment costs when they are present or assuming they are present when they are not. To do so, it helps to break-down the different contributions to the maximum expected $NPV_i$ when employing the optimal policy $\bf{h_i}^*$ versus when employing the policy that would be optimal were there no costs to policy adjustment $\bf{h_0}^*$. For example, if we take the first of the adjustment penalty forms, $\Pi_1$
\begin{equation}
 NPV_i( \mathbf{h_1^*} ) = \sum_{t=0}^\infty (\overbrace{ p h^*_{1,t}-c_0E^*_{1t}}^{[1]}-\overbrace{c_1 | h^*_{1,t}- h^*_{1,t-1}|}^{[2]} ) \displaystyle \frac{1}{(1+\delta)^t}
\end{equation}
and 
\begin{equation}
 NPV_i( \mathbf{h_0^*} ) = \sum_{t=0}^\infty (\underbrace{ p h^*_{0,t}-c_0E^*_{0t}}_{[3]}-\underbrace{c_1 | h^*_{0,t}- h^*_{0,t-1}|}_{[4]} ) \displaystyle \frac{1}{(1+\delta)^t}
\end{equation}

Histograms for the different contributions labelled $[1]-[4]$ here when taken across XXX replicate runs are shown are shown in Figure 5 (contribution $[1]$ red, $[2]$ green, $[3]$ blue, and $[4]$ mauve). The cost of assuming policy adjustments are present when in fact they are absent is given by subtracting the contribution to the first infinite sum from term $[1]$ from the contribution to the second infinite sum of term $[3]$ (red-blue in the Figure). (Note that convergence properties required to do this are met because we assume a positive discount rate). This cost is positive because the optimal controls recommended when assuming policy adjustment costs are present do not track variations in stock size as closely. Therefore, this harvesting strategy provides lower net revenue dockside.

In contrast, the cost of ignoring policy adjustment costs when in fact they are present is given by subtracting the second infinite sum from the first (contributions $([1]-[2])-([3]-[4]))$ in the equations. These costs are positive because the lost revenues from not tracking stock variations as closely are smaller than the penalties of policy adjustment that are incurred if managers try to track stock variations more tightly.
